---
title: "The Seafood Globalization Lab's Template Report"
subtitle: "To support reproducible open-science workflows"
author: 
  - name: Author Name
    orcid: 0000-0000-0000-0000
    email: email
    affiliations:
      - name: University of Washington
  - name: Author Name
    orcid: 0000-0000-0000-0000
    email: email
    affiliations:
      - name: University of Washington
date: last-modified
date-format: "YYYY-MM-DD"
theme: cosmo 
number-sections: true
title-block-banner: TRUE
format: 
  html: 
    toc: true
    self-contained: true
    page-layout: full
    code-fold: true
    code-tools: true
    code-line-numbers: true
execute:
     echo: false
     include: false
     warning: false
---

## What is This Document? 

This is a Quarto Document meant to serve as an report template for the Seafood Globalization Lab. 
We outfitted this document with 3 key parts for a reproducible and open-science workflows: 

1. A `YAML` header with some basic document metadata and settings. 
2. A reliable way to manage software package and versioning using the `pak` package. 
(see the `setup-pkgs` code chunk below and the `./00_write_pkg_deps.R` file)
3. An example of how one can name and organize their directory paths (see `setup-params-paths-funs`)

### Tips

- Put every new sentence in markdown on a new code line. Git tracks changes line-by-line, so this will give your document `git diff`s the most detailed resolution. 
- If you are going to have multiple lengthy sections, think about knitting together child quarto docs to break up the report and compile into larger document. 
- Name code blocks similarly to good file naming conventions (*e.g.* `setup-pkgs` and `setup-params-paths-funs` show a user the blocks are related but do different things).
The code block names can be used to navigate the document in the Rstudio or Positron document outline. 
Set with the `#| label:` code block option.

### More Resources

1. [The official Quarto Documentation](https://quarto.org/docs/guide/)
2. [Quarto: The Practical Guide](https://quarto-tdg.org/)
3. [The NCEAS Learning Hub's coreR Course book](https://learning.nceas.ucsb.edu/2024-10-coreR/session_05.html)
4. Reach out to a human and setup a consult or brainstorm session. 

## Connect to the Lab's Server

The Lab maintains a UW server to share and store datasets and analyses. 
You will likely need to connect to the server using the instructions below and code similar to the `setup-params-paths-funs` code block in this document. 

**If you are on the UW campus:**

- Log onto the `gephartlab.fish` server (see lab manual for more details)
- Map the server to your local machine [(UW instructions here)](https://uwconnect.uw.edu/it?id=kb_article_view&sysparm_article=KB0034311)

**If you are remote:**

- Log onto the Husky OnNet VPN [(UW instructions here)](https://uwconnect.uw.edu/it?id=kb_article_view&sysparm_article=KB0034243)
- Map the server to your local machine [(UW instructions here)](https://uwconnect.uw.edu/it?id=kb_article_view&sysparm_article=KB0034311) 


```{r}
#| label: setup-pkgs

# make Posit package manager primary install repo (uses faster binaries)
# @ snapshot date - hold all package versions to the "latest" version at this date
# Think about updating this date, but a few months delayed from "today" to avoid release bugs
pak::repo_add(CRAN = "RSPM@2025-10-31")

# install packages
pak::pak(c(
  "arrow",
  "dplyr",
  "tidyr",
  "glue"
))
# load packages
{
  library(arrow)
  library(dplyr)
  library(tidyr)
  library(glue)
}

```

```{r}
#| label: setup-params-paths-funs

# Set data parameters
artis_version <- "1.2"
artis_prod_type <- "FAO"

# set analysis parameters
analysis_hs_version <- c("HS17")
analysis_year <- c(2020)

# point to UW NAS gephartlab.fish server from MacOS 
# may require VPN connection and mapping the server to local computer
path_artis_dir <- "/Volumes/gephartlab/data-storage/artis"
path_analysis <- "/Volumes/gephartlab/analyses/your-analysis-folder"

# Construct data paths
path_artis <- file.path(path_artis_dir, glue("ARTIS_v{artis_version}_{artis_prod_type}_database_KNB"))
path_artis_ref_tbls <- file.path(path_artis, "reference_tables")


# read in custom functions 
source("00_functions.R")

```
